---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_Xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

Abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```


# Introduction 

China's overseas development financing now surpasses that of the United States, the World Bank, and several other multilateral development and lending institutions combined. As the reach and scope of its development activities continue to grow, the motives behind its overseas activities remain hotly contested, and the limited transparency surrounding Beijing's overseas financing only fuels the controversy. China neither reports its foreign aid spending to international organizations, as do Development Assistance Committee (DAC) members to the OECD, nor does China publish its aid expenditures in a public database, as does the United States in USAID's *Greenbook*. For this reason, many Western governments assume Beijing deliberately tries to keep its international development finance a secret [@fuchsRudyak2019]. 

Thankfully, due to the painstaking work of researchers to document and analyze trends in China's development financing, both academics and policymakers have learned a great deal about Beijing's approach to giving and lending. Although Beijing has primarily focused on its immediate surrounding neighbors in the Asia-Pacific region and Central Asia with respect to its geostrategic interests, it is increasingly thinking and behaving in global terms [@nathan&scobell2012]. When it comes to Beijing's overseas giving and lending, far from the rogue donor that many have feared, China's ODA-like expenditures follow patterns similar to those of OECD-DAC donors [@dreherEtAl2022]. Hence, much like these traditional donors, China's foreign aid presents as a versatile foreign policy tool through which Beijing seeks to accomplish strategic and economic objectives in international politics, promote public goods in developing countries, and generate goodwill and support stronger diplomatic relations abroad. 

However, the discovery that China is little different from traditional Western donors makes the limited state-sanctioned transparency of its overseas development financing all the more puzzling. Many of the goals often attributed to Western donors (generating goodwill, strengthening diplomatic ties, etc.) are difficult to accomplish in secret. And, while Beijing has taken steps to improve the visible branding of its aid projects on the ground, there is limited evidence that this is sufficient for attributing credit to Beijing [see @dietrichEtAl2018]. This therefore raises a natural question. *Does China’s overseas development financing relate to public diplomacy and international recognition? If so, how?*

We propose that despite the lack of formal reporting, Beijing can pursue recognition and diplomacy with its overseas financing with the help of other complementary foreign policy activities. Past research has shown that two specific instruments may play special roles in complementing these foreign policy objectives. First, international media are one way that countries can generate attention and promote a positive spin on their activities in foreign audiences. As @nye_public_2008-2 notes, daily communications that reach both domestic and foreign populations are a way to improve a country's soft power. Perhaps in recognition of this, Beijing has expanded its outward facing state sponsored media activities and news reporting over the past two decades. This has been done in part through the English version of *Xinhua*, China's top state sponsored news agency.

Second, aside from news media, China engages in more conventional forms of bilateral diplomacy via government-to-government diplomatic missions. Efforts to document Beijing's public diplomacy have revealed an expansive set of activities in which Beijing engages.^[See @aidData2021.] These range from the financial to the cultural, and from elite-to-elite meetings to informational exchanges.

While public diplomacy and outward-facing state-sponsored media are not solely used to support China's overseas development financing, we believe they have clear overlapping purposes. In particular, diplomacy and coverage are critical *visible* activities that can compensate for the often opaque character of Beijing's development finance. Thus, to the extent that China's development finance is targeted at image-building and diplomatic activities, we hypothesize that recipients of China's overseas development assistance will also be disproportionate targets of media coverage in the English version of *Xinhua* (to support China's image and to build publicity around its development activities) and be more frequent hosts of diplomatic missions from Beijing (to support closer bilateral diplomacy and cooperation).

As we test these hypotheses, in our research design we take care to ensure that we delineate China's development financing according to the types of assistance China offers. Until recently, many have mistakenly conflated Beijing's ODA-like giving with its other official financing (OOF). However, efforts to disentangle China's activities with respect to grants and low-interest loans (financing that would meet the OECD definition of official development assistance or ODA) from its activities with respect to higher interest loans and export credits (OOF) have unmasked a considerable divergence in goals. The conventional view is that while *aid* (ODA) is closely tied to Beijing's foreign policy goals, *debt* (OOF) is related to Beijing's commercial interests.^[See @dreherEtAl2022.] Thus, as we test our hypotheses, we also distinguish between Beijing-as-donor from Beijing-as-lender.

The results from the analysis provide a novel perspective on the ways that China applies additional instruments to complement the goals it pursues via its overseas development financing. However, while the findings overall are consistent with our hypotheses, they do so in ways that also problematize the neat distinction between China's use of aid and its use of debt. In particular, we find that *Xinhua* coverage is disproportionately concentrated among China's ODA recipients, while no significant relationship exists between aid and diplomatic visits. Conversely, we find that debt is significantly linked to a greater frequency of bilateral diplomatic missions from Beijing, but no significant difference in *Xinhua* coverage. Together these findings reveal an intriguing pattern: Beijing likes to talk about its aid recipients but prioritizes diplomacy with its debtors.

Aid recipient countries disproportionately get more media attention from *Xinhua* to report their economy and needs for development projects and aid. Notably, *Xinhua* does not just promote China’s efforts to offer aid to those countries in need but also gives a rounded picture of those countries’ economic conditions that justify their bases of needs. Another implication of our finding is that Beijing is more likely to lend money to its “friends”: countries with more cordial diplomatic relations tend to have closer political interests and ties. While the previous study highlights that lending indicates Beijing’s economic interests, our finding suggests that lending is more closely related to its political interests. For instance, Russia, one of China’s closest allies, receives the highest amount of lending on average among 142 countries but no aid at all between 2002 and 2017. In contrast, Iraq shows the opposite pattern: it receives the highest amount of aid from China during the period of our investigation, but it does not receive any loans. 

\clearpage

# Some Stylized Facts

Figure 1 shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017. Values are shown in millions of 2017 USD. Blue shows values for aid and red shows values for debt. The difference in China's application of debt relative to aid is stark, and the gulf only expands over time. The observed explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century, as others have documented. Burdened with vast foreign currency reserves due do years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreherEtAl2022]. This focus spurred a radical change in China's development finance portfolio. As @dreherEtAl2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5). Figure 1 shows this transformation from donor to lender in the starkest of terms.

```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
library(knitr)
library(here)
include_graphics(
  here('06_figures/aid_debt_trends.png')
)
```

```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status.'}
include_graphics(
  here('06_figures/rate_coverage_visits_by_aid.png')
)
```

```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country debtor status.'}
include_graphics(
  here('06_figures/rate_coverage_visits_by_debt.png')
)
```

```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
include_graphics(
  here('06_figures/dev_countries_over_time_by_type.png')
)
```

\clearpage 

# Results

```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
include_graphics(
  here('06_figures/neg_binom_estimates.png')
)
```


```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
include_graphics(
  here('06_figures/predicted_differences.png')
)
```



\clearpage

# References