---
title: "Descriptive analysis 2"
author: "Lucie Lu"
date: "2022-08-05"
output: pdf_document
---

```{r}

rm(list = ls())
library(tidyverse)
library(dplyr)
#install.packages("censReg")
#library(censReg)
#library(AER)
#library(texreg)
library(estimatr)
library(mgcv)
library(here)
#install.packages("OneR")
library(OneR)
theme_set(theme_light())

```

```{r, eval=F}

dt <- read_csv(
  "https://raw.githubusercontent.com/milesdwilliams15/chinese_media_and_foreign_aid/main/01_data/final_data/final_data_imputed.csv"
)

```


## Which countries recevie the most aids on average?
```{r}
library("dplyr")
# aid only
filter(new_dt, type == "Aid")

aid_average <- new_dt %>% group_by(recipient) %>% summarise_at(vars(aid), list(mean_of_aid = mean))
od_aid_average <- aid_average[order(aid_average$mean_of_aid, decreasing = T), ]

od_aid_average$rank_aid <- rank(-od_aid_average$mean_of_aid, ties.method = "max")
od_aid_average
```
Iraq gets the most aids (aids from humanitarian aids)

## Which countries receive the most aids and debts?

```{r}

debt_average <- new_dt %>% group_by(recipient) %>% summarise_at(vars(debt), list(mean_of_debt = mean))

od_debt_average <- debt_average[order(debt_average$mean_of_debt, decreasing = T), ]

od_debt_average$rank_debt <- rank(-od_debt_average$mean_of_debt, ties.method = "max")
od_debt_average
```
```{r}
top_20_recipients <- cbind((od_debt_average %>% filter(rank_debt <= 20))[,1], 
      (od_aid_average %>% filter(rank_aid <= 20))[,1]) 
colnames(top_20_recipients) <- c("debt_top20", "aid_top20")
top_20_recipients 

overlap0 <- calculate.overlap( x = list("debt" = top_20_recipients$debt_top20, 
                                        "aids" = top_20_recipients$aid_top20))
overlap0$a3
```

## Interesting patterns
Top 20 debt and aids countries are shown above. 8 countries have overlaps: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya,Sudan are listed both.

```{r}
od_debt_average %>% filter(rank_debt == 142) #no debts
od_aid_average %>% filter(rank_aid == 142) #no aids

c_no_debt <- (od_debt_average %>% filter(rank_debt == 142))$recipient
c_no_aid <- (od_aid_average %>% filter(rank_aid == 142))$recipient

```


```{r}
#install.packages("VennDiagram")
library(VennDiagram)
overlap <- calculate.overlap( x = list( "aids" = top_20_recipients$aid_top20, 
                                        "debt" = c_no_debt))
overlap
```

Russia has most debts, but no aids; Iraq has most aids, but no debts at all. 

## Which countries receive the most aid and debt? And their proportions?
```{r}

# calculate sum of aid and debt for each row
for (i in 1:nrow(new_dt)) {
   new_dt$aids_plus_debts[i] <- new_dt$aid[i] + new_dt$debt[i]
}

aid_debt_both <- new_dt %>% group_by(recipient) %>% 
  summarise_at(vars(aids_plus_debts), list(mean_of_both = mean))

##########

# combine aid average and aid debt both data
aid_prop <- merge(aid_average, aid_debt_both, by = "recipient")
aid_prop$mean_aid_prop <- round(aid_prop$mean_of_aid/aid_prop$mean_of_both, digits=2)

# combine debt average and aid debt both data

debt_prop <- merge(debt_average, aid_debt_both, by = "recipient")
debt_prop$mean_debt_prop <- round(debt_prop$mean_of_debt/debt_prop$mean_of_both, digits=2)

```

```{r informative combination of aid and debt data}
## merge with ordered aid debt both average data

m1 <- merge(aid_debt_both, aid_prop,  by = "recipient")
m2 <- merge(m1, debt_prop, by = "recipient")
m2 <- m2[,-c(2,4)]


m2 <- m2[order(m2$mean_of_both, decreasing = T), ]
m2$rank_both <- rank(-m2$mean_of_both, ties.method = "max")
m2

```

The proportion of debts is much higher than the aids for the top recipients.

## Which countries receive nothing?

```{r}
# 8 countries never receive anything
filter(m2, rank_both == 142)
```

8 countries never receive anything from China: Curacao, Dominican Republic, El Salvador, French Polynesia, Guam, Nicaragua, Panama and Praguay.

```{r combine media and diplomatic visits}
m2_figure <- m2

m3 <- cbind(new_dt %>% group_by(recipient) %>% summarise_at(vars(counts_by_year), list(coverage = mean)),
  new_dt %>% group_by(recipient) %>% summarise_at(vars(total_visits), list(diplomatic_visits = mean)))

m3 <- m3[,-3]

m2_figure <- merge(m2_figure, m3, by = 'recipient')

m2_figure <- m2_figure[order(m2_figure$coverage, decreasing = T), ]
m2_figure$rank_coverage <- rank(-m2_figure$coverage, ties.method = "max")
m2_figure
```

```{r}
top_20_coverage <- (m2_figure %>% filter(rank_coverage <= 20))[,1]
top_20_recipients$coverage_top20 <-  top_20_coverage
top_20_recipients
```

```{r overlaps}

overlap2 <- calculate.overlap( x = list( "aids" = top_20_recipients$aid_top20, 
                                        "coverage" = top_20_recipients$coverage_top20))
overlap2$a3

overlap3 <- calculate.overlap( x = list( "aids" = top_20_recipients$debt_top20, 
                                        "coverage" = top_20_recipients$coverage_top20))
overlap3$a3

```
- Countries that show up on the top 20 aid-recipients and Xinhua coverage are: Iraq, Indonesia, Pakistan, Cambodia, Kenya and Zambia.

- Countries that show up on the top 20 debt-recipients and Xinhua coverage are: Russia, Brazil, Indonesia, Pakistan, Vietnam, Malaysia, Iran, Cambodia, Kenya.

```{r}

lm1 <- lm(mean_of_debt ~ Coverage, data=m2_figure)
summary(lm1)
```